Target Markdown

### 2024-01-10 _targets.Rmd
Update SEM figure

```{r}
label_sem <- as.character(as.roman(seq_len(nrow(sem_simplified_bivariate_relations))))
p_sem_simplified_bivariate_relations <-
  plot_grid(
    plotlist = sem_simplified_bivariate_relations$plot,
    label_x = 1, hjust = 1.0,
    labels = label_sem
  )
sem_file <- here("report", "figures", "sem_stab_simplified.pdf")
p_sem <- ggdraw() +
  draw_image(magick::image_read_pdf(sem_file, density = 600),
    x = 0, y = 0,
    width = 1, height = 1,
    hjust = 0, halign = 0, valign = 0
  )
p_sem_tot <- plot_grid(
  p_sem, p_sem_simplified_bivariate_relations,
  nrow = 2, rel_heights = c(.6, 1),
  labels = "auto"
)
ggsave_multiple(
  paste0("p_sem_tot", c(".png", ".pdf")),
  plot = p_sem_tot,
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * 1.6,
  units = "mm")
```

```{r}
ggsave_multiple(
  paste0("p_sem_bivariate_relations", c(".png", ".pdf")),
  plot = tar_read(p_sem_bivariate_relations),
  path = here::here("report", "figures"),
  scale = 3,
  dpi = 400,
  width = 80,
  height = 80 * .9,
  units = "mm")
```

@@

```{r}
p_sem_fig <- plot_grid(
  p_sem, p_sem_simplified_bivariate_relations,
  print(
    p_sem_tot_stab +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
      ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top"),

      )
    ),
  nrow = 3, rel_heights = c(.7, 1, .6),
  labels = "auto"
)
ggsave_multiple(
  paste0("p_sem_fig", c(".png", ".pdf")),
  plot = p_sem_fig,
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * 2.0,
  units = "mm")
```

>>>>

```{r}
label_sem <- as.character(as.roman(seq_len(nrow(sem_simplified_bivariate_relations))))
p_sem_simplified_bivariate_relations <-
  plot_grid(
    plotlist = sem_simplified_bivariate_relations$plot,
    label_x = 1, hjust = 1.0,
    labels = label_sem
  )
sem_file <- here("report", "figures", "sem_stab_simplified.pdf")
p_sem <- ggdraw() +
  draw_image(magick::image_read_pdf(sem_file, density = 600),
    x = 0, y = 0,
    width = 1, height = 1,
    hjust = 0, halign = 0, valign = 0
  )
p_sem_tot <- plot_grid(
  p_sem, p_sem_simplified_bivariate_relations,
  nrow = 2, rel_heights = c(.6, 1),
  labels = "auto"
)
ggsave_multiple(
  paste0("p_sem_tot", c(".jpg", ".png", ".pdf")),
  plot = p_sem_tot,
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * 1.6,
  units = "mm")
```

```{r}

ggsave_multiple(
  paste0("p_sem_simplified_bivariate_relations", c(".jpg", ".png", ".pdf")),
  plot = p_sem_simplified_bivariate_relations + theme(axis.title = element_text(size = 7)),
  path = here::here("report", "figures"),
  scale = 3.5,
  dpi = 300,
  width = 70,
  height = 70 * .9,
  units = "mm")
```

@@

```{r}
bivariate_rel_file <- here("report", "figures", "p_sem_simplified_bivariate_relations.jpg")
p_bivariate_rel <- ggdraw() +
  draw_image(magick::image_read(bivariate_rel_file, density = 300),
    x = 0, y = 0,
    width = 1, height = 1,
    hjust = 0, halign = 0, valign = 0
  )

p_sem_fig <- plot_grid(
  p_sem, p_bivariate_rel,
  print(
    p_sem_tot_stab +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
      ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top"),

      )
    ),
  nrow = 3, rel_heights = c(.7, 1, .6),
  labels = "auto"
)

p_sem_fig <- plot_grid(p_sem,
  print(
    p_sem_tot_stab +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
      ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top"),

      )
    ),
  p_bivariate_rel,
  NULL,
  nrow = 2, rel_heights = c(.7, 1),
  labels = c("a", "b", "c", ""),
  align = "h", axis = "tblr"
)
ggsave_multiple(
  paste0("p_sem_fig", c(".png", ".pdf")),
  plot = p_sem_fig,
  path = here::here("report", "figures"),
  scale = 3.4,
  dpi = 400,
  width = 80,
  height = 80 * .8,
  units = "mm")
```
